%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, letterpaper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.4cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-skyblue}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{false}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{./examples/profile}

\name{}{\large Khaled Z. Ibrahim}
\position{Computer Scientist{\enskip\cdotp\enskip}Computational Research
Division{\enskip\cdotp\enskip} Lawrence Berkeley National Laboratory}
\address{
One Cyclotron Road, 059-4024N, M/S 59R4104, Berkeley, CA 94720}

\mobile{(510)679-9139}
\email{kzibrahim@lbl.gov}
\homepage{crd.lbl.gov/departments/computer-science/CLaSS/staff/khaled-ibrahim}
%\github{posquit0}
%\linkedin{posquit0}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \extrainfo{extra informations}

%\quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Computer Scientist Hiring Committee}
  {2575 Sand Hill Road, Menlo Park, CA 94025}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
%\lettertitle{Job Application for Software Engineer}

% How the letter is opened
\letteropening{Dear SLAC hiring committee,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae, Research Statement}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Khaled Z. Ibrahim~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

I am submitting my resume and research statement for your consideration for the 
computer scientist/senior scientist position (Job \#: 2157).
Currently, I am a tenured computer scientist at Lawrence Berkeley
National Laboratory in the Computer Languages \& Systems Software
(CLaSS) Group,  and an affiliate of the computer architecture (CAG) and the
performance and algorithm (PAR) groups.

My research interests include both basic computer science (parallel
architecture and runtime systems) and  
cross-disciplinary activities, such as optimizing simulation codes of quantum chromodynamics
simulation, turbulence in plasma
fusion, and  quantum chemistry using tensor contractions. 

For performance analysis and
tuning research, I targeted multi/many-core architectures (e.g., Intel Haswell, Intel KNC/KNL),
GPU-accelerated architectures (e.g., nVidia GPUs), and light-weight
many-core architectures (e.g., IBM BGQ). 
Moreover, I  contributed to optimizing communication runtimes including
MPI and GASNet,  improving their performance on many-core architectures and virtual computing
environments. I conducted research in
architecting power-efficient embedded designs and high-performance
speculation mechanisms for parallel processing.

In addition to best paper awards, I won the HPC Challenge Award for the best FFT performance on 49K cores
Mira in Supercomputing 2014 (runner up for GUPS and HPL),  and two
top-ten positions in Graph500 in
Supercomputing 2016. I helped develop and 
scale plasma turbulence simulation to 98K cores and scaled coupled cluster
(CCSD) computation to tens of thousands of cores. 
Leveraging years of research in parallel architectures, runtime systems, and application
performance tuning, I adopt cross-layer optimization strategies to push the performance
boundary on extreme-scale   supercomputers.  

%and I am a believer of cross-layer optimization strategies for best
%performance and efficiency.


By joining SLAC, I aim  to advance the computational performance and efficiency in future
exascale computing systems in various scientific research disciplines, 
including elementary particle physics, and astrophysics and cosmology. I have always had  the aspiration for
putting computational resources as a vehicle for scientific discoveries.

I believe the post-Moore's law computing era will significantly impact HPC
computing. Specifically, current  trends for constructing efficient
architectures would significantly influence the strategies for scientific code development. 
In my research statement, I share my views on how to achieve
and maintain leadership in scientific discoveries in the exascale era and beyond. 

I would be glad to provide further details if my skills match the position. 
{\bf I also hope  to maintain confidentiality in processing my
application.} 

%Thank you for considering my application,

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
