
%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvskills}

  \vspace{1mm}
%---------------------------------------------------------
  \cvskill 
    {Linux Fake Webcam} % Category
    {Wrote a hacky program in C allowing users to impersonate anybody on webcam chat. The program inputs any video file and a corresponding JSON file of timestamps. The GUI allows users to smoothly and convincingly control the actions of a virtual person or thing on their webcam. I achieved this by writing a Linux Kernel Module (using V4l2 API) and a corresponding application (using Libav) to pipe video into a webcam device.} % Skills
  \vspace{1mm}
%---------------------------------------------------------
  \cvskill
    {GoGaucho UCSB App} % Category
    {Backend developer for iOS and Android app with 3000+ daily users. In charge of Python/Flask code that scrapes UCSB's class registration website, as well as scraping Shuttle Live Locations for convenient access inside the App.} % Skills
%---------------------------------------------------------
\cvskill
    {Masterlock Solver Bot} % Category
    {Built a robot which is able to unlock any master combination lock in seconds and output its combination. I designed a custom breadboard circuit, wrote Arduino code, 3D printed a frame, and assembled together with motors.} % Skills
  \vspace{1mm}
%---------------------------------------------------------
\cvskill
  {Neural Network Game Bot}
  {Developed an AI player in Javascript using neural networks and evolutionary learning algorithms. The bot learns how to complete any level of a platformer game (similar to mario) given only the game controls and end destination.}
  \vspace{1mm}
%---------------------------------------------------------
  \cvskill
    {LISP interpreter in SNAP} % Category
    {Designed an interpreter for LISP in SNAP (a visual programming language) in an attempt to loophole the requirement of using a visual language for in-class projects by instead using the LISP written language.} % Skills
  \vspace{1mm}

\end{cvskills}
