%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, letterpaper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.4cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-skyblue}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{false}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{./examples/profile}

\name{}{\large Seif Ibrahim}
\position{Computer Science Student{\enskip\cdotp\enskip} UC Santa Barbara}
\address{6850 El Colegio Rd APT \#9406, Santa Barbara, CA 93117}

\mobile{(510)612-0049}
\email{seifibrahim10@gmail.com}
\github{seifibrahim}
\linkedin{seif-ibrahim-71475b163}
%\homepage{crd.lbl.gov/departments/computer-science/CLaSS/staff/khaled-ibrahim}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \extrainfo{extra informations}

%\quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
{Apple Hiring Committe}
{Apple Inc. \\
One Infinite Loop \\
Cupertino, CA 95014}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
%\lettertitle{Cover Letter for SoC Internship}

% How the letter is opened
\letteropening{Dear Apple hiring committee,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Seif Ibrahim~~~·~~~Cover Letter}
  {\mbox{}}

% Print the title with above letter informations
  \makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

I am submitting my resume and application for your consideration for the SoC System Level Test Engineer Intern position. When I learned of your opening for the system-on-chip position, I felt compelled to send in my application. With my 5+ years of experience in C/C++ and work with microcontrollers, I am confident my skills will be of benefit to Apple's mission to build high-performance and elegant processors. 

Currently, I am a Computer Science Student in UC Santa Barbara's College of Creative Studies --- a small class (of about 6 people) on an accelerated track through Computer Science curriculum and research. I am looking to gain work experience in Computer Science at Apple this summer. 

I am obsessed with the elegant, simple, and fast. My favorite programming language is C. I am an avid ViM nerd and Debian Linux user. My understanding of computers extends below the level of the compiler and operating system; as a result, I've participated in CTF challenges and written device drivers for Linux requiring an understanding of memory layout and machine code. Solving online algorithm challenges on USA Computing Olympiad, Project Euler, CodeChef, etc. is one of my favorite pastimes --- to the point that my friends and family can't understand how I can spend hours writing and debugging the same program without getting frustrated. 

My experience also extends to working with robotics and microcontrollers. As president of my high school's robotics club, I wrote most of the software for the Arduino and Beaglebone microcontrollers that run the robot. I was able to lead my team to victory in a high-pressure competition environment, as well as develop my leadership and teamwork skills. I have also worked on personal projects involving programming and debugging Arduino C code --- these are detailed in my resume. With my years of experience in just writing and debugging code, I have established a natural workflow which allows to find and fix errors very quickly and makes writing code more intuitive to me. This is an advantage that I have noticed, has propelled me over many of classmates.

With my technical skills and my deep interest in high-performance and low-level systems, I believe that I could quickly surpass your expectations as an intern at Apple. I urge you to take a look at my resume.

Thank you for your consideration.
\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
